### 2020-02-06 README.Rmd
Adjust the size of the logo.
experimetal examination of topic-intrusion

# oolong <img src="man/figures/oolong_logo.png" align="right" height="150" />

@@

The goal of oolong (烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia. It is very popular in Taiwan, Japan and Hong Kong) is to generate and adminstrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.

>>>>

# oolong <img src="man/figures/oolong_logo.png" align="right" height="200" />

@@

The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia. It is very popular in Taiwan, Japan and Hong Kong] is to generate and adminstrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
